Jug: Software for Reproducible Computation

### 2012-04-25 paper.tex
TXT Contextualize jug wrt incpy

However, unlike make, jug is written in Python and tasks can consist of any
Python function and its arguments. A jugfile (the file which specifies which
tasks need to be run---named by analogy to the makefiles of make) is a simple
Python script with some added notations (we will see just how little changes
need to be made from a conventional Python script).

\section{Design Choices}
\subsection{Task Based Architecture}

@@

\section{Discussion}
Unlike most previous tools for reproducible research, jug focuses on the
development of the computation as much as its communication. In fact, when it
comes to communication other tools might be better suited as they combine
written exposition with computer code. They can be used in combination with jug
as they do not often provide caching and distribution, needed for large
projects. While the simplest mode of jug use is to have a single
\textit{jugfile}, a jugfile can import the results of another. For example, a
first jugfile might perform all heavy-duty computation and be run on a
computing cluster. A second script could be embedded inside an executable paper
to generate tables and plots \citep{Delescluse2011}. This faster script could
be run as part of building the paper (while the longer script would take too
long).

>>>>

However, unlike make, jug is written in Python and tasks can consist of any
Python function and its arguments. A jugfile (the file which specifies which
tasks need to be run---named by analogy to the makefiles of make) is a simple
Python script with some added notations (we will see just how little changes
need to be made from a conventional Python script).
\section{Design Choices}
\subsection{Task Based Architecture}

@@

\section{Discussion}

\subsection{Similar Tools}

Of interest, is also the \textsc{IncPy} implementation of a Python interpreter
with automatic persistent memoization~\cite{Guo_IncPy,Guo_IncPy_pre}. The
arguments made for that system apply to Jug as well, with a few differences.
Their system implements automatic memoization, while, using Jug, the user needs
to automatically annotate functions to memoize using \texttt{TaskGenerator}.
This extra control can be necessary to avoid a proliferation of intermediate
results when these are very large (often a very large intermediate output is
not necessary, and only a summary must be kept). Additionally, Jug supports
running tasks in parallel, a functionality that is absent from \textsc{IncPy}.

\subsection{Conclusions}

Unlike most previous tools for reproducible research, jug focuses on the
development of the computation as much as its communication. In fact, when it
comes to communication other tools might be better suited as they combine
written exposition with computer code. They can be used in combination with jug
as they do not often provide caching and distribution, needed for large
projects. While the simplest mode of jug use is to have a single
\textit{jugfile}, a jugfile can import the results of another. For example, a
first jugfile might perform all heavy-duty computation and be run on a
computing cluster. A second script could be embedded inside an executable paper
to generate tables and plots \citep{Delescluse2011}. This faster script could
be run as part of building the paper (while the longer script would take too
long).
